### 2019-12-03 thesis.tex
small correction

In the end, we have four appendices. \Cref{appA} depicts an improved
approximation for the second order susceptibility of the electrostatic
bremsstrahlung for Langmuir waves. In \Cref{appB} we discuss the
similarities of the asymptotic equilibrium state of the Langmuir waves
spectrum, considering a combination of an inverse power-law kappa
distribution and a Maxwellian distribution, in the presence and the
absence of the electrostatic bremsstrahlung effect. The discussion in
\Cref{appB} is related to the article appended in \Cref{appC}, which
is parallel research and is only slightly connected to the main subject
of this work. \Cref{master} shows the paper that summarizes the results
of my Master’s dissertation, which may be considered the starting point
of this doctoral research. % \Cref{appE} explores relevant aspects of
% current solar physics research and how they are connected to this work.
% It was written to be more like a light, informative reading, than a
% deep academic digression.

@@

Therefore, we have two distinct situations. One is the situation in which
collective modes are not important, and the electric field energy can be
expressed by Eq. \eqref{balance} with the electric field fluctuation
$\left< \delta E^2 \right>_{{\bf k},\omega}^0$ given by \eqref{field-fluc}.
The other is standard situation, in which collective modes are important,
and the wave electric field is determined by
\begin{equation}
  \label{collective}
  \begin{split}
  \left< \delta E^2 \right>_{{\bf k},\omega}
  -\left< \delta E^2 \right>_{{\bf k},\omega}^0
  &=\sum_{\sigma=\pm 1}\sum_{\alpha=L,S}
    I_{\bf k}^{\sigma \alpha}\delta(\omega-\sigma \omega_{\bf k}^\alpha)\\
  \mbox{Re}\, \epsilon({\bf k},\sigma\omega_{\bf k}^\alpha)&=0.
\end{split}
\end{equation}

@@

\section{Collisional damping rates for plasma waves}
\label{coll-damp}
In this first analysis, presented in Ref. \cite{Tigik2016b}, we have
numerically integrated Eqs. \eqref{gammaL}
% LFZ190822: O artigo está anexado, mas acho que mesmo assim vale dizer qual
% é o artigo na lista de referências. Algo como
% "In this first analysis, presented in Ref. \cite{Tigik...}, 
% we have numerically integrated Eqs. \eqref{gammaL} for ..."
% Sabrina: ok
for $L$ waves, and \eqref{gammaS} for $S$ waves, considering Maxwellian
velocity distribution function for the particles, without including the
new effects in the time evolution subroutine. The main objective here
was to comprehend important aspects of this so-far unknown expressions,
how they relate to other equivalent plasma processes and with the
heuristic Spitzer formula, for collisional damping. The main question
was: ``Are they equivalent?'', more specifically, ``Are their magnitudes,
at least, in the same order of magnitude?''. The answer was no. We found
out that the Spitzer formula overestimates the collisional damping effect
in several orders of magnitude in comparison with the new expression.
Further, the insignificance of the collisional damping became even more
evident when we compared its damping rate with the collisionless (Landau)
damping rate in the same figure.

@@

Furthermore, an extra result is presented in \Cref{appB}, where
we compare the stationary state of the $L$ waves spectrum obtained
after the time evolution (using the results discussed in \cite{
  Tigik2016a}), with the asymptotic Langmuir spectrum generated by
a theoretical core-halo distribution, composed $95\%$ by a Maxwellian
core and $5\%$ by a kappa tail, in the presence and in the absence of
bremsstrahlung emission, for several values of the $\kappa$ index. It is
shown that the asymptotic spectra obtained in the case of distributions
with low $\kappa$ indexes are less affected by the electrostatic
bremsstrahlung emission than the spectra generated in the presence of
higher $\kappa$ indexes, and in the Maxwellian case. These findings
suggest that core-halo distributions may represent the asymptotic
equilibrium when the electrostatic bremsstrahlung is taken into account.

@@

For use in this asymptotic equation, let us assume isotropic distributions
for ions and electrons, which are the summation of Maxwellian and kappa
distributions. In terms of dimensionless variables, we have
\begin{equation}
\label{fbeta}
f_{\beta}({\bf u})= \left(1-\frac{n_{\kappa\beta}}{n_e}\right)
\frac{1}{\pi^{3/2} u_{\beta}^3}\exp\left(-\frac{u^2}{u_\beta^2}\right)
+\frac{n_{\kappa\beta}}{n_e}\frac{1}{\pi^{3/2} \kappa_\beta^{3/2}
u_{\beta,\kappa}^3}
\frac{\Gamma(\kappa_\beta+1)}{\Gamma(\kappa_\beta-1/2)}
\left(1+\frac{u^2}{\kappa_\beta u_{\beta,\kappa}^2}
\right)^{-(\kappa_\beta+1)}~.
\end{equation}
where
\begin{equation}
u_{\beta,\kappa}= \frac{v_{\beta,\kappa}}{v_e},\quad
u_\beta=\frac{v_\beta}{v_e},\quad
u_{\beta,\kappa}^2= \frac{\kappa_\beta-3/2}{\kappa_\beta} u_\beta^2.
\end{equation}

>>>>

In the end, we have four appendices. \Cref{appA} depicts an improved
approximation for the second order susceptibility of the electrostatic
bremsstrahlung for Langmuir waves. In \Cref{appB} we discuss the
similarities of the asymptotic equilibrium state of the Langmuir waves
spectrum, considering a combination of an inverse power-law Kappa
distribution and a Maxwellian distribution, in the presence and the
absence of the electrostatic bremsstrahlung effect. The discussion in
\Cref{appB} is related to the article appended in \Cref{appC}, which
is parallel research and is only slightly connected to the main subject
of this work. \Cref{master} shows the paper that summarizes the results
of my Master’s dissertation, which may be considered the starting point
of this doctoral research. % \Cref{appE} explores relevant aspects of
% current solar physics research and how they are connected to this work.
% It was written to be more like a light, informative reading, than a
% deep academic digression.

@@

Therefore, we have two distinct situations. One is the situation in which
collective modes are not important, and the electric field energy may be
expressed by Eq. \eqref{balance} with the electric field fluctuation
$\left< \delta E^2 \right>_{{\bf k},\omega}^0$ given by \eqref{field-fluc}.
The other is the standard situation, in which collective modes are important,
and the wave electric field is determined by
\begin{equation}
  \label{collective}
  \begin{split}
  \left< \delta E^2 \right>_{{\bf k},\omega}
  -\left< \delta E^2 \right>_{{\bf k},\omega}^0
  &=\sum_{\sigma=\pm 1}\sum_{\alpha=L,S}
    I_{\bf k}^{\sigma \alpha}\delta(\omega-\sigma \omega_{\bf k}^\alpha)\\
  \mbox{Re}\, \epsilon({\bf k},\sigma\omega_{\bf k}^\alpha)&=0.
\end{split}
\end{equation}

@@

\section{Collisional damping rates for plasma waves}
\label{coll-damp}
In this first analysis, presented in Ref. \cite{Tigik2016b}, we have
numerically integrated Eqs. \eqref{gammaL}
% LFZ190822: O artigo está anexado, mas acho que mesmo assim vale dizer qual
% é o artigo na lista de referências. Algo como
% "In this first analysis, presented in Ref. \cite{Tigik...}, 
% we have numerically integrated Eqs. \eqref{gammaL} for ..."
% Sabrina: ok
for $L$ waves, and \eqref{gammaS} for $S$ waves, considering Maxwellian
velocity distribution function for the particles, without including the
new effects in the time evolution subroutine. The main objective here
was to comprehend important aspects of these so-far unknown expressions,
how they relate to other equivalent plasma processes and with the
heuristic Spitzer formula, for collisional damping. The main question
was: ``Are they equivalent?'', more specifically, ``Are their magnitudes,
at least, in the same order of magnitude?''. The answer was no. We found
out that the Spitzer formula overestimates the collisional damping effect
in several orders of magnitude in comparison with the new expression.
Further, the insignificance of the collisional damping became even more
evident when we compared its damping rate with the collisionless (Landau)
damping rate in the same figure.

@@

Furthermore, an extra result is presented in \Cref{appB}, where
we compare the stationary state of the $L$ waves spectrum obtained
after the time evolution (using the results discussed in \cite{
  Tigik2016a}), with the asymptotic Langmuir spectrum generated by
a theoretical core-halo distribution, composed $95\%$ by a Maxwellian
core and $5\%$ by a Kappa tail, in the presence and in the absence of
bremsstrahlung emission, for several values of the $\kappa$ index. It is
shown that the asymptotic spectra obtained in the case of distributions
with low $\kappa$ indexes are less affected by the electrostatic
bremsstrahlung emission than the spectra generated in the presence of
higher $\kappa$ indexes, and in the Maxwellian case. These findings
suggest that core-halo distributions may represent the asymptotic
equilibrium when the electrostatic bremsstrahlung is taken into account.

@@

For use in this asymptotic equation, let us assume isotropic distributions
for ions and electrons, which are the summation of Maxwellian and Kappa
distributions. In terms of dimensionless variables, we have
\begin{equation}
\label{fbeta}
f_{\beta}({\bf u})= \left(1-\frac{n_{\kappa\beta}}{n_e}\right)
\frac{1}{\pi^{3/2} u_{\beta}^3}\exp\left(-\frac{u^2}{u_\beta^2}\right)
+\frac{n_{\kappa\beta}}{n_e}\frac{1}{\pi^{3/2} \kappa_\beta^{3/2}
u_{\beta,\kappa}^3}
\frac{\Gamma(\kappa_\beta+1)}{\Gamma(\kappa_\beta-1/2)}
\left(1+\frac{u^2}{\kappa_\beta u_{\beta,\kappa}^2}
\right)^{-(\kappa_\beta+1)}~.
\end{equation}
where
\begin{equation}
u_{\beta,\kappa}= \frac{v_{\beta,\kappa}}{v_e},\quad
u_\beta=\frac{v_\beta}{v_e},\quad
u_{\beta,\kappa}^2= \frac{\kappa_\beta-3/2}{\kappa_\beta} u_\beta^2.
\end{equation}
